### 2022-11-12 NSF2022/Description/backgroundv2.tex
BGv2 done

\subsection{Applications}
Since the formulation is scale independent, it can be applied broad
range of nonspecific self-organization phenomena in surface chemistry,
biology and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly.
For example,
three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure~\ref{fig:flow_map}).
Moreover, a simple change
of boundary conditions from amphiphilic,
to biased hydrophobic, to polar
results in distinct equilibrium morphologies
(Figure~\ref{fig:self-assembly2}).
Some further applications are
(i) Chemistry: Janus spheres Since
the formulation is scale independent, it can represent a suspension of
amphiphiles, where the granules represent the mean properties of a small
collection of lipids, at the nanoscopic scale. For larger scales, the
representation is literal and the granules Janus spheres.
(ii) Pickering emulsion
(iii) \todo[inline]{Bertozzi's problem}
(iv) Tension driven microprinting
(v) Vesicle hydrodynamics.

>>>>

\subsection{Applications}
Since the formulation is scale independent, it can be applied broad
range of nonspecific self-organization phenomena in surface chemistry,
biology and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly.
For example,
three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure~\ref{fig:flow_map}).
Moreover, a simple change
of boundary conditions from amphiphilic,
to biased hydrophobic, to polar
results in distinct equilibrium morphologies
(Figure~\ref{fig:self-assembly2}).
Further applications include
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
